THESIS PROJECT PROPOSAL

### 2019-11-02 project_ashish/paper.tex
Update paper.tex

The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. As there 
is strong destructive inteference in the t-channel for the standard model couplings, this production mode is sensitive to both the sign 
and the magnitude of any coupling beyond the SM between Higgs boson and top quark caused by higher dimensional operators in effective SM 
theory.

>>>>

The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. The 
anomalous coupling will arise when we add interaction terms (dimension 6 operators in effective SM theory) in the Higgs potential. As 
there is strong destructive inteference in the t-channel for the standard model couplings, this production mode is sensitive to both the 
sign and the magnitude of any coupling beyond the SM between Higgs boson and top quark induced by higher dimensional operators in 
effective SM theory.
